\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.6in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor}
\usepackage[super]{nth}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{textcomp}
\hypersetup {
    colorlinks=true,
    linkcolor=colorlink,
    filecolor=magenta,      
    urlcolor=colorlink,
}

\name{Rounak Datta}
\address{ \href{mailto:rounakdatta12@gmail.com}{rounakdatta12@gmail.com} \hspace{2pt} \\ \hspace{2pt} \href{https://rounakdatta.github.io}{rounakdatta.github.io} \hspace{2pt} \\ \hspace{2pt}   \faicon{github}/\href{https://github.com/rounakdatta}{rounakdatta} \hspace{2pt} \\ \hspace{2pt} \href{tel:+919432201722}{+91 9432201722}}
\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

\begin{rSection}{Education}
  \begin{rEmptySubsection}{\href{https://www.srmist.edu.in/}{SRM Institute of Science and Technology}}{Chennai, India}{B.Tech, Computer Science, CGPA: 8.90/10}{Jul `16 - May `20}
  \end{rEmptySubsection}

\end{rSection}

\begin{rSection}{Experience}

  \begin{rSubsection}{\href{https://commandk.dev}{CommandK}}{Bengaluru, India}{Founding Engineer (Backend, Infrastructure)}{Aug `22 - Mar `24}
    \item Collaborated in the zero-to-one building of a modern secrets and configuration management platform. From \textbf{decoupled RBAC} to \textbf{infra-as-code} in Pulumi, from \textbf{Kubernetes operators} to \textbf{cloud-native admission-controllers}, got the chance to wear multiple hats from platform engineering to API development.
    \item Successfully navigated the intricacies of architecting \textbf{multi-cloud deployments}, both on-premise and hosted.
          \end{rSubsection}

  \begin{rSubsection}{\href{https://tech.hotstar.com}{Disney+ Hotstar}}{Bengaluru, India}{Software Development Engineer I \textrightarrow II (Data Platform, Growth Engineering)}{Jul `20 - Jul `22}
    \item Designed \& implemented a \textbf{streaming data quality framework} which validates incoming events at the ingestion layer; built its self-serve tooling (visual schema editor), CLI complements and at-rest data quality suite.
    \item Addressed a wide range of production incidents wearing the \textbf{on-call engineer} hat (including mega events \textbf{IPL} '20, '21, '22); across self-hosted Hive/Spark/Kafka/Flink/Presto.
    \item Took lead in implementing our re-architected \textbf{Change-Data-Capture framework} (CDC) to improve parallelization, configurability, reliability and data-freshness; introduced GitOps into Airflow CDC pipelines.
    \item Led the foundational efforts in \textbf{Growth Engineering} team to enable Data Platform, Subscriptions \& Payments services to new markets in South-East Asia; introduced major refactors (like async customer-facing APIs) to the subscriptions partnership framework which cut down new onboarding times by over 80\%.
    \item Designed and architected a fault-tolerant backend for supporting \textbf{Android in-app-payments} for subscriptions across India and SEA apps.
    \item Drove the development and release of the highly extensible framework behind \textbf{Disney+ Worldwide Pre-Launch \& Landing experience}.
      \end{rSubsection}

  \vspace*{-\baselineskip}

  \begin{rSubsection}{}{}{Intern (Data Platform) \textrightarrow PPO}{June `19 - Jul `19, Jan `20 - Jun `20}
    \item Designed and developed a \textbf{storage-layer resource optimization} framework, which when benchmarked achieved xx\% improvements in query times and x\% reductions in data lake storage costs.
    \item Crafted a batch \textbf{data metrics collection} job, greatly enabling visibility and static monitoring of data sanity.
      \end{rSubsection}

  \begin{rSubsection}{\href{https://www.guvi.in/}{Guvi Geek Networks}}{Chennai, India}{Intern (team of two)}{Mar `18 - Jul `18, Dec `18}
    \item Built out the first iteration of Guvi 2.0 platform, an \textbf{adaptive learning platform} (via rule-based algorithms).
    \item Developed an in-house \textbf{resume parsing} system with sub-second retrieval latency for 20K+ entities; our software supports a diverse range of resume formats. Released as OSS [\textbf{\href{https://github.com/rounakdatta/resxme}{\faicon{github}}}].
    \item Architected an English \textbf{spelling \& grammatical corrector} using classical NLP methods; achieved around 73\% accuracy when benchmarked with Grammarly \& human proofreading. Released as OSS [\textbf{\href{https://github.com/rounakdatta/correctly}{\faicon{github}}}].
      \end{rSubsection}

\end{rSection}

\begin{rSection}{Strengths}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages   & Kotlin, Java, Go, Python, OCaml, Nix                            \\
    Databases               & PostgreSQL, MySQL; Prometheus, InfluxDB; Apache Hive         \\
    Frameworks              & Apache Spark, Apache Kafka, Spring Framework; Pulumi, Terraform \\
    Application Development & Android SDK, Ionic Cordova, ReactJS                     \\
  \end{tabular}
\end{rSection}

\begin{rSection}{Selected Projects}
  \textbullet\ \textbf{\textsf{GoDFS}} [\textbf{\href{https://rounakdatta.github.io/posts/godfs}{\faicon{link}}}] [\textbf{\href{https://github.com/rounakdatta/GoDFS}{\faicon{github}}}] - Implemented a  toy distributed filesystem in Go. Handled the aspects of hearbeat \& secondary namenode for fault tolerance; packaged as Docker Compose.

  \textbullet\ \textbf{\textsf{Argus (PagerDuty for Things)}} [\textbf{\href{https://rounakdatta.github.io/posts/pagerduty-for-iot}{\faicon{link}}}] [\textbf{\href{https://github.com/rounakdatta?tab=repositories&q=argus}{\faicon{github}}}] - An IoT project exhibiting continuous monitoring of fluid level and automated alerting on mobile devices. From ESP32 firmware development (C) to backend service (Go) to cross-platform app (Ionic Cordova), I solo-developed it all.

  \textbullet\ \emph{Open-source contributions} include projects like \textbf{\textsf{Gopass}} [\textbf{\href{https://github.com/gopasspw/gopassbridge}{\faicon{github}}}], \textbf{\textsf{Android-Password-Store}} [\textbf{\href{https://github.com/android-password-store/Android-Password-Store}{\faicon{github}}}], \textbf{\textsf{Apache Airflow}} [\textbf{\href{https://github.com/apache/airflow}{\faicon{github}}}].

\end{rSection}

\end{document}
